---
title: "Markdown Leaflet"
author: "P.Y.Fong"
date: "`r format(Sys.Date(),'%d %B %Y')`"
output:
  html_document:
    fig_width: 10
    fig_height: 10
---

```{r setup, include=FALSE}
library (knitr)
opts_chunk$set(cache.lazy= T,
               echo = T,
               message=F,
               warning=F,
               comment="")
```
##      1.0 Executive Summary

Created a web page using R Markdown that features a map showing major population centres in Malaysia created with the Leaflet package. 
Hosted the webpage on either RPubs.  
The webpage must contain the date the document was created, and it must contain a map created with Leaflet.  
An attempt at Creativity was made!

##      2.0 Libraries
```{r Libraries}
library(dplyr)
library(leaflet)
library(maps)
library(tidyr)
library(RColorBrewer)
```

##      3.0 Selecting Larger Population Centres in Malaysia
```{r load data}
data("world.cities") # Using world.cities data set from library(maps)
str(world.cities)
```

Examining the structure of world.cities the variables of interest are from columns 1 & 3:5.  
Reducing the dataset and filtering for population centres >100,000
```{r Malaysia}
Malaysia <- world.cities %>%
  filter(country.etc == "Malaysia" & pop > 100000) %>%
  select(-c(capital,country.etc))
Malaysia
```

##      4.0 The Map
A suitable heading was created followed by a color palette.  
Leaflet layers were then built up to create the final map:  

1.    Leaflet map of the Malaysia data frame.

2.    Add default OpenStreetMap map tiles.

3.    Add Circle markers of size and color matching population numbers.

4.    Add Legend with suitable heading.

```{r mapping}
heading<- paste("Malaysia - Major Population Centres", " (", as.character(format(Sys.Date(), '%d %B %Y')), ")")
pal <- colorBin(palette = "Dark2", domain = Malaysia$pop)

leaflet(data = Malaysia) %>%
  addTiles() %>%
  addCircleMarkers(~long, ~lat, popup = ~pop, label = ~name,
                   radius= ~pop/50000, fillColor = ~pal(pop),
                   color="Purple", fillOpacity = 0.5, weight= 1) %>%
  addLegend(position= "topright", pal= pal, values = ~pop,
            group = "circles", title= heading)